Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
box 1 edits

Varying social scales can have different fitness repercussions for individuals.
Rhesus macaques (*Macaca mulatta*) had higher survivorship when they had fewer
but stronger and more stable social associates and grooming partners rather than
simply more associates [@Ellis_2019]. Furthermore, it is a common trope that
individuals must be associating to interact, and many studies assume that
proximity is proxy for interacting [@Farine_2015a]. For instance, baboons need
to be in proximity to groom each other. Certain animals use interactions that do
not require proximity such as long-distance vocalization or olfactory signals
[@Carter_2015]. It is possible to record social interactions that do not require
proximity, for example using microphone arrays to construct long-distance
communication networks [@Snijders_2017]. Our results indicate varying social
patterns in different habitat types, potentially suggesting different types
of interactions. Higher graph strength in forage and open habitats may 
be an indication of caribou using visual cues not possible in forest habitats
(Figure \@ref(fig:socres)).

Changing social phenotypes over ontogeny can affect fitness [@Berger_2015; @Brent_2017].
Temporal scale is important as individuals progress through development at 
different rates [@Tarka_2018] and this variation can complicate the selection of 
time windows. Considering fine temporal scales provide insight across
developmental stages that may otherwise be missed [@Turner_2017].

Thus, it is
critical to carefully consider the temporal scale that is meaningful for the
proposed hypotheses.

Multilayer networks enable researchers to look at similarities and differences
between explicit stages of ontogeny, seasons or other temporal windows

Multilayer networks provide unique opportunities and challenges, linking these
various scales, for understanding the social phenotypes and environments of
individuals and their fitness outcomes.

Multilayer network
metrics could be used to assess the relationship between an individual’s social
phenotype and fitness.

It would also be a meaningful reduction of many
network metrics that could help simplify statistical analyses and deal with the
frequent correlations between social network metrics in different types of
networks [@Castles_2014].

Furthermore, multilayer networks provide a framework
to test hypotheses linking social phenotypes and fitness across temporal scales.
Because of the non-independent nature of social interactions and associations,
especially over time, it is hard to test hypotheses about social dynamics with a
suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
multilayer networks, making layers of different temporal periods provides a way
to make appropriate null models to test questions about the dynamics of an
individual’s social network position over multiple aggregated time periods.

In both mono- and multilayer networks, 
the effect of
scale on the relationship between an individual’s social network position and
fitness need to be considered based on the hypotheses being tested and
logistical constraints.
<!-- previous version -->

<!-- TODO: retrieve from prev versions -->
Monolayer network approaches have been increasingly used to link social network
position with individual fitness, including in primates [@Brent_2017;
@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
for understanding fitness consequences in the context of social network
positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
@Holekamp_2011].

Selection of appropriate time windows is essential for capturing sociality in specific
life stages of interest. Social phenotypes can change over ontogeny in ways that
can affect fitness [@Berger_2015; @Brent_2017]. 
Further complicating the issue,
individuals can vary in their rate of development [@Tarka_2018]. This variation
can make defining the appropriate temporal scale for testing the fitness
implications of an individual’s social phenotype over different stages of
ontogeny difficult.  However, considering fine temporal scales has been show to
provide insight across developmental stages that may otherwise be missed
[@Turner_2017] <!-- It would be better to cite the more recent one if it gets released in time. -->

>>>>

Varying social scales can have different fitness repercussions for individuals.
Rhesus macaques (*Macaca mulatta*) had higher survivorship when they had fewer
but stronger and more stable social associates and grooming partners rather than
simply more associates [@Ellis_2019].  It is a common trope that
individuals must be associating to interact, and many studies assume that
proximity is proxy for interacting [@Farine_2015a]. For instance, baboons must be 
within proximity of each other for grooming yet other animals use interactions that do
not require proximity such as long-distance vocalization or olfactory signals
[@Carter_2015]. It is possible to record social interactions that do not require
proximity using, for example, microphone arrays to construct long-distance
communication networks [@Snijders_2017]. Our results indicate varying social
patterns in different habitat types, potentially suggesting different types
of interactions. Higher graph strength in forage and open habitats may 
indicate that caribou use visual or other cues not relevant in forest habitats
(Figure \@ref(fig:socres)).

Multilayer networks enable researchers to look at similarities and differences
between discrete temporal windows. 
Changing social phenotypes over ontogeny can affect fitness [@Berger_2015; @Brent_2017].
Individuals progress through development at 
different rates [@Tarka_2018] and this variation can complicate the selection of 
time windows. Considering fine temporal scales provides insight across
developmental stages that may otherwise be missed [@Turner_2017]. Thus, it
is critical to carefully consider the effect of
scale on the relationship between an individual’s social network position and
fitness using a temporal scale based on the hypotheses being tested and
logistical constraints.

Multilayer networks provide a framework
to test hypotheses linking social phenotypes and fitness across temporal scales.
Because of the non-independent nature of social interactions and associations,
the selection of a suitable null model  to test hypotheses about social dynamics with a
suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
multilayer networks, making layers of different temporal periods provides a way
to make appropriate null models to test questions about the dynamics of an
individual’s social network position over multiple aggregated time periods.

network metrics that could help simplify statistical analyses and deal with the
frequent correlations between social network metrics in different types of
networks [@Castles_2014].
